Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

>>>>

The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two tunables of Hardness
Manipulation.

(4) \ul{Parameters in $g_\mathsf{LGA}$ and $g_\mathsf{B}$.}

A constant $u$ is used to normalize the loss value of the previous training
iteration $\ell_{t-1}$ into $\bar{\ell}_{t-1}\in[0,1]$.
%
The constant is empirically selected as $u=\gamma$ in our experiment.
%
According to our observation, the loss value will quickly decrease below
$\gamma$, and will remain in the $[0,\gamma]$ range for the whole training
process.
%
If we set $u$ to a larger constant than $\gamma$, the normalized loss
$\bar{\ell}_{t-1}$ will be smaller, and results in stronger adversarial
examples through HM and harms the model performance on benign examples.

A parameter $\xi$ is used by $g_\mathsf{B}$ to slightly boost a given
$H_\mathsf{D}$ calculated from another benign triplet.
%
As mentioned in the experiments section, $\xi$ is set to $0.1$ in our
experiment.
%
We refrain from conducting further parameter search because $g_\mathsf{B}$
is only proposed to demonstrate that the problem in the late phase of
training can be alleviated in our step-by-step description of our approach.
%
And $g_\mathsf{B}$ does not alleviate the problem in the early phase of
training, and hence it does not belong to Graduate Adversary.
%
The function $g_\mathsf{B}$ is not a key point.

Our LGA function $g_\mathsf{LGA}$ reuses the triplet margin parameter $\gamma$
in order to remain in the range of Semihard, \ie, $-\gamma<g_\mathsf{LGA}<0$.
%
Apart from this, LGA is parameter-free.

(5) \ul{Weight constant $\lambda$ of ICS loss term $L_\text{ICS}$.}

The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on SOP.
%
As demonstrated in the experiments, there is a trade-off between robustness and
performance on benign examples when tuning the $\lambda$ parameter.
%
Our experiments demonstrate that the ICS loss term is effective in improving
adversarial training efficiency and model robustness, but in practice, the
adopters of our method may need to re-evaluate the trade-off between
performance and robustness, and ajudst $\lambda$ accordingly.
